On Combinatorial Games and de Bruijn Sequences

### 2016-09-29 infdebruijn.tex
.

\begin{proposition}\label{advanced-pos}
	For a given $w \in L_n$, let $l$ be the number of trailing zeros (from the left) in $w$ and let $\bar{w}=b_1(w)$. Then For all $n-k \leq i \leq n-1$ the word $\rr{\bar{w}}{i}$ comes $i-(n-|f_3(u)| \pmod n)$ letters before the first $u \in \T{0^{m-1} (\bar{w}_{m} + 1) \bar{w}_{m+1}\cdots \bar{w}_n}_{m=i}^{n}$ such that $u \in L_n$ and  $\max\{u_1,\dots,u_{n-1}\} \leq max(w)$.
\end{proposition}

>>>>

\begin{proposition}\label{advanced-pos}
	For a given $w \in L_n$, let $l$ be the number of trailing zeros (from the left) in $w$ and let $\bar{w}=b_1(w)$. Then, for all $|w|-l \leq i \leq n-1$ the word $\rr{\bar{w}}{i}$ comes $i-(n-|f_3(u)| \pmod n)$ letters before the first $u \in \T{0^{m-1} (\bar{w}_{m} + 1) \bar{w}_{m+1}\cdots \bar{w}_n}_{m=i+1}^{n}$ such that $u \in L_n$ and  $\max\{u_1,\dots,u_{n-1}\} \leq max(w)$.
\end{proposition}
